\section{Research Plan:}

\indent The research for this project will begin with setting up the FPGA platform that will be used for development.
This process includes installing software and setting up the core firmware image. After development platform is
operational, I will research best known methods of system optimization that can be implemented in firmware. A key
focus of this effort will be on power efficiency. I will then begin the first phase of firmware design to enable control
of the image sensor and system clock. The second phase of firmware design will focus on control mechanisms for image system
processing. System integration will be the focus of the third phase of firmware design and will focus on integrating the
image sensor, system clock, and image system processing control mechanisms. The goal by May 2nd is to have firmware up
and running that has effective control of the image sensing frame rate. Sufficient testing of the integrated system will be
conducted to gain understanding of potential optimizations and system limitations. I will then consult with Dr. LiKamWa and Dr.
Turaga about conducting the vision analysis of the data captured by the system. After developing understanding of the vision
analysis, I will speak with medical professionals about specific image capture tasks that can provide useful data for motion
analysis. The system will then be tuned to effectively conduct the image capture tasks of interest. The findings of my research
will then be compiled into a formal research paper.
